Ms. No. PSRM-OA-2019-0126.R1 entitled ``Taking Dyads Seriously''

### 2021-02-03 revisionMemo2/rev1.tex
push up memo revisions

		We thank the reviewer for taking the time to provide their comments and helping us to make the manuscript more focused. We have made a number of changes to the framing of the article per the reviewer's suggestions, these appear throughout the manuscript, but especially on pages X.

@@

		Thank you for the suggestion, we have made this change on page X.

@@

		agree that in the case of nonparametric or semiparametric models ... but this is not what most

@@

		intervals are produced via a gibbs sampler ...

@@

		we compare with a vanilla ols ...
		and then the other set of results in the appendix re aranow use their dyad clustered approach ... per your request from last time

@@

>>>>

		We thank the reviewer for taking the time to provide their comments and helping us to make the manuscript more focused. We have made a number of changes to the framing of the article per the reviewer's suggestions. Additionally, we have significantly modified the introduction and removed what could be considered as, but certainly not intended, swipes at other literatures. The editor also suggested a number of changes to be made in the introduction and we have adopted those as well. We disagree with the choice of removing the introduction completely and starting with section 2 because we feel some relatively non-technical context will be useful to more general readers.

@@

		We thank R1 for this suggestion, per R1's first comment, we have actually removed this from the introduction and clarified the goal of the paper along the lines of what R1 and the editor suggested.

@@

		These are fair questions especially in terms of the complications that arise when using nonparametric or semiparametric models. Instead of trying to resolve all this in the introduction, we have removed the portion of the introduction that led the reviewer to ask this question.

@@

		Bayesian inference for the parameters from the AME model proceed via Gibbs sampling algorithms where we iteratively simulate values of the model parameters from their full conditional distributions. We have added additional discussion about how the parameters are estimated to both the simulation section and the applications. In Appendix A we provide a brief outline of the MCMC algorithm used. We do not re-derive the full conditional distributions for the AME models in this paper as it has been done in previous work that we have cited: Hoff 2005, 2008; Minhas et al. 2019. Additionally, Hoff (2021), which we now cite in the paper, more fully details the history of the AME model and how it has evolved since its original formulation in Hoff et al. (2002).

@@

		Given the various forms of network dependence that can arise it's not clear to us how to actually construct an analytical calculation like what R1 is suggesting. If the purpose of this analytical calculation would be to highlight the consequences that dyadic dependence would have in the context of inference, then that is exactly why we open Section 2 in the paper with a discussion of the assumptiong underlying GLMs. }}
		In terms of the simulation section, we thank R1 for pointing out the parts that are still unclear and have added in their suggested language with respect to clarifying the standard IR approach.

@@

		We thank R1 for asking a question about how confidence intervals are produced because that was an error on our part as we meant to say credible interval. Within our framework These are generated directly from the posterior distribution generated from the three models. Specifically, for every simulation and model we calculate the 95\% credible interval and then across all simulations we estimate the proportion of times that the true value fell within those intervals. We have clarified this in the simulation section of the manuscript.}}
